User-level Grid Monitoring with Inca 2

### 2007-02-27 papers/hpdc-gmw-2007/paper.tex
added summary
added note about scalability not yet being implemented

corrected NGS deployment

added acknowledgement section so we don't forget


git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6584 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

Inca was designed to distribute control and storage workload among
multiple Inca components if needed.  For example, one depot could forward
storage requests and queries to another depot to distribute its workload or to
maintain a mirror for fault tolerance.  Figure~\ref{tg_coord_fig} shows a more
complex scenario where two Inca deployments coordinate with each other.  For
example, application communities like GEON have their own Grid but also have
access to resources on TeraGrid.   Two separate Inca deployments can result in
duplicate testing. Instead, one Inca deployment can coordinate the execution
of a suite with another deployment.
Figure~\ref{tg_coord_fig} shows this type of coordinated deployment, where Grid B 
has its own resources but also has access to resources in Grid A.
When an Inca administrator submits a suite to Grid B, the Inca agent running
on Grid B will determine which reporters run on Grid A resources and forward
them as a suite request to Grid A's agent.  If Grid B has permission to submit
suites, Grid A's agent will execute the suite and configure its depot to
forwards results back to Grid B's depot.

@@

NGS currently has Inca 2 deployed on 8 resources to verify their Grid services 
and compilers.  They have wrapped the GITS~\cite{gits} tests using a new
API developed by the GITS developer.  The GITS reporters include 17 tests, 
such as small job submissions and data transfers, that verify Globus and GSI-SSH functionality.
NGS also has 12 tests for their compilers and
utilize 2 security reporters from the Inca repository.

@@

~\newpage

>>>>

Inca was designed to distribute control and storage workload among
multiple Inca components if needed.  For example, one depot could forward
storage requests and queries to another depot to distribute its workload or to
maintain a mirror for fault tolerance.  Figure~\ref{tg_coord_fig} shows a more
complex scenario where two Inca deployments coordinate with each other.  For
example, application communities like GEON have their own Grid but also have
access to resources on TeraGrid.   Two separate Inca deployments can result in
duplicate testing. Instead, one Inca deployment can coordinate the execution
of a suite with another deployment.
Figure~\ref{tg_coord_fig} shows this type of coordinated deployment, where Grid B 
has its own resources but also has access to resources in Grid A.
When an Inca administrator submits a suite to Grid B, the Inca agent running
on Grid B will determine which reporters run on Grid A resources and forward
them as a suite request to Grid A's agent.  If Grid B has permission to submit
suites, Grid A's agent will execute the suite and configure its depot to
forwards results back to Grid B's depot.  Forwarding is not yet implemented 
in Inca 2.

@@

NGS currently has Inca 2 deployed on four resources to verify their Grid services (on eight sites) and compilers.  They have wrapped the GITS~\cite{gits} tests using a new
API developed by the GITS developer.  The GITS reporters include 17 tests, 
such as small job submissions and data transfers, that verify Globus and GSI-SSH functionality.
NGS also has 12 tests for their compilers and
utilize 2 security reporters from the Inca repository.

@@

%1.  Motivate and differentiate the Grid monitoring Inca does 2. Describe Inca
%2 design and its benefits 3. Illustrate that Inca 2 design is mature and
%being used in production by several Grids 4. Be different from Inca 1 paper
The goal of user-level Grid monitoring is to test and measure the Grid
infrastructure from an impartial user perspective and detect problems before
users notice them.  Inca 2 implements such a user-level Grid monitoring system
and provides a number of new and improved features over our first version,
Inca 1.  The architecture and features of Inca 2 enable an Inca administrator
to easily write and deploy tests and performance measurements to Grid
resources and maintain them in a changing Grid environment.  The storage,
archiving, and querying capabilities also enable in-depth analysis of Grid
errors and performance now in a historical context, which will benefit Grid
operators and system administrators.  Inca 2 also provides a number of
security features such as short-term proxy management and supports
scalability.  A production version of Inca 2 was released in February 2007 and
has been used in production environments to verify the common user environment
of TeraGrid and to execute and collect data for a set of Grid benchmarks on
both TeraGrid and GEON.  Future enhancements of Inca 2 will improve its fault
tolerance and enable more in-depth analysis of the overall Grid health and
behavior.  They should also make it easier to resolve, in addition to detect
errors and understand them in a historical context.  The features that Inca
provides and its proposed enhancements should improve the stability of the
Grid infrastructure it monitors, ultimately improving the productivity of
scientists who conduct research on a Grid.

%------------------------------------------------------------------------- 
\Section{Acknowledgements}
